### 2022-02-24 paper/localpsf.tex
updating paper based on advances the last couple months. Work in progress...

\begin{equation}
	\phi_x(y) \approx \phi_{x_i}(y)
\end{equation}

>>>>

Consider the following approximations:
\begin{align}
	\phi_x(y) &\approx \phi_{x_i}(y) \label{eq:translate1}\\
	\phi_x(y) &\approx \phi_{x_i}(y-x+x_i) \label{eq:translate2}\\
	\phi_x(y) &\approx \phi_{x_i}\left(y-\mu(x)+\mu(x_i)\right). \label{eq:translate3}
\end{align}

First one: low rank. Second one: local translation invariance/product-convolution. Third one: our proposal.

Approximation \eqref{eq:translate3} is an improvement upon \eqref{eq:translate1} and \eqref{eq:translate2} that generalizes them both. If \eqref{eq:translate1} holds, then $\mu(x) \approx \mu(x_i)$, and so \eqref{eq:translate3} holds. If \eqref{eq:translate2} holds, then $\mu(x_i)-\mu(x) \approx x_i - x$ because translating a distribution translates its mean, so again \eqref{eq:translate3} holds.

the first one holds, then $\mu(x) = \mu(x_i)$, and so the third one holds. If the second one holds, then $\mu(x) - \mu(x_i) = x - x_i$, and so the third one holds.

Notice that the shift of the
